---
title: "My dynamic report"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```


```{r}
library(tidyverse)
library(magick)
```

```{css}
.dynamic-comment {
background-color: lightpink;
             }
body {
     background-color:lightblue;
    }   
```

```{r banner, echo=FALSE,out.width='100%'}


# public transport images for header

  img1 <- image_read("train_image.jpg")

  img2 <- image_read("bus_image.png")

# image resize for header 
   img1 <- image_resize(img1, "600x")   # height 600px
   img2 <- image_resize(img2, "600x")


# Combine side-by-side
  combined <- image_append(c(img1, img2))
   combined
```



```{r}
 logged_data <- 
  read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQYGExy9W6fvAkpM0dOwyXbS2WUJt9UC_dQbsco_SzreXDE7eLLRL6Vv6IG-8BD-xLRYYAzGiQvRYl1/pub?gid=1667279551&single=true&output=csv")

 # logged_data using the rename() function, 
# as part of creating a new data frame named latest_data.
 
 # Rename the variables to create new df named latest data

 latest_data <- logged_data %>%
     rename(transport_to_uni = `What method of public transport did you take to university today?`,
     commute_to_uni_minutes = `How long did your trip to university take today (in minutes)?`,
     transport_from_uni = `What method of  transport did you take after leaving university today?`,
     commute_from_uni_minutes = `How long did your trip take from university? (in minutes)`,
     day = `What day of the week is this observation for?`,
     delay = `Was your public transport delayed today? (select all that apply)`,
     student_status = `Which of the following apply to you?`
       )
  
 
# Bar chart 1 What is the most common commute method to university
 
latest_data %>%
  ggplot(aes(x = transport_from_uni, fill = transport_from_uni)) +
  theme_light() +
  geom_bar() +
  scale_fill_manual(values = c( # To change each bar plot colour, I searched for the tidyverse package functions online.
    "bus" = "#FF69B4",
    "train" = "#32CD32",
    "both bus and train" = "#1E90FF" 
  )) +
  labs(
    title = "Transport methods to University",
    subtitle = "What is the most common commute method?",
    x = "Transport Type",
    y = "Number of Students"
  )


#Bar Chart 2, When are public transport delays most common for university students?

latest_data %>%
           ggplot() +
           theme_light()+
           geom_bar(aes(x = delay, fill = delay)) + 
           # bar chart
           scale_fill_manual(values = c(  # manual colour assignment, saw this one online
             "yes (leaving university)" = "#FFC0CB",
             "yes (going to university)" = "#90EE90",
             "yes (going to university), yes (leaving university)" = "lightblue",
             "no" = "lightyellow")) +
           labs(
             title = "To and From University",
             subtitle = "When are public transport delays most common for university students?",
             x = "Delay",
             y = "University Student Observations"
                 )

#Bar Chart 3 Time it takes for students to arrive  on campus via public transport"

latest_data %>%
     ggplot() +
    theme_light()+
    geom_bar(aes(y = commute_to_uni_minutes),
    fill = "#FFC0CB") + 
    labs(
    title = "Commute Time to University in Minutes",
    subtitle = "Time it takes for students to arrive  on campus via public transport",
    x = "University Student Observations",
    y = "Minutes"
    )
  min_commute_from <-    min(latest_data$commute_from_uni_minutes)
  
  
 
  
```

## Dynamic Comments of Summary Statistics
  


The longest commute time from university in minutes reported by the students who completed the survey was `r max(latest_data$commute_from_uni_minutes, na.rm = TRUE)`.

The longest commute time to university in minutes reported by the students who completed the survey was `r max(latest_data$commute_to_uni_minutes, na.rm = TRUE)`.





The mean_commute time to Univeristy in minutes reported by University students who completed the survey was `r latest_data$commute_to_uni_minutes %>% mean(na.rm = TRUE) %>% round(1)`.

## What is this dynamic report tracking?

This dynamic report is tracking observations of university students’ commutes to and from university who use public transport in Auckland.

## What's going on with this data?

My dynamic report is tracking the differences in public transport commute methods among university students. I wanted to see if factors like taking the bus or train, commute length, and delays impact how frequently students travel to and from university.

## The nature of your data: What am I analysing?

I am analysing commute and transport habits for university students. I collected this data through a Google Form, which I shared with my friends and also completed myself with my own observations. I designed the form so that each submission reflects a full day of commuting to and from university.


